Clustering in a hyperbolic model of complex networks.

### 2019-03-12 concentration_argument.tex
improvements to section 4.2 and typos in Lemma 6.6

Note that since all three corollaries follow from Lemma~\ref{lem:concentration_argument}, Proposition~\ref{prop:concentration_argument_all} follows if we can prove that the conclusions from this lemma holds when we replace $\rho(y,k_n)$ with either $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$. For this the following, slightly more general version of Lemma~\ref{lem:concentration_argument} will be important.

\begin{lemma}\label{lem:concentration_argument_rho_approximation}
Let $\alpha > \frac{1}{2}, \nu > 0$, $k_n \to \infty$ be such that $k_n = \smallO{n}$, $\ell_n = (1 + \epsilon_n)k_n$, with $\epsilon_n \to 0$ and define
\[
	\lambda_n^\pm = (\ell_n \pm C \sqrt{\ell_n \log(\ell_n)}) \wedge \xi, \quad \text{and} \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi}\right).
\] 
In addition, define $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, where $\hat{\mu}_n(y)$ satisfies, 
\[
	\hat{\mu}_n(y) = (1 + \phi_n(y))\mu(y),
\]
where $\phi_n(y)$ is a continuous differentiable function such that
\begin{enumerate}[\upshape i)]
\item For some $0 < \varepsilon < 1$, $\displaystyle \lim_{n \to \infty} \sup_{0 \le y \le (1 - \varepsilon)R_n} |\phi_n(y)| = 0$,
\item $\displaystyle \lim_{n \to \infty}  \sup_{y \in \Kcal_{C}(\ell_n)} |\phi_n^\prime(y)| = 0.$
\end{enumerate}
Then the following holds.
\begin{enumerate}
\item For any continuous function $h : \R_+ \rightarrow  \R$, such that $h(y) = \bigO{e^{\beta y}}$ as $y \to \infty$ for some $\beta < \alpha$, 
\begin{equation}\label{eq:error_bound_int_rho_approx_not_K}
	\int_{\R_+ \setminus (a_n^-, a_n^+)} \hat{\rho}_n(y,k_n) h(y) \alpha e^{-\alpha y} \dd y
	= \bigO{k_n^{-(1+C^2)/2}},
\end{equation}
as $n \to \infty$.
\item If in addition, $h(a_n) \sim h(b_n)$ whenever $a_n \sim b_n$, as $n \to \infty$. Then,
\begin{equation}\label{eq:concentration_h_rho_approx}
	\int_0^\infty h(y) \hat{\rho}_n(y,k_n) \alpha e^{-\alpha y^\prime} \dd y^\prime \sim  
		2\alpha \xi^{2\alpha} h(2\log(k_n/\xi)) k_n^{-(2\alpha + 1)},
\end{equation}
as $n \to \infty$.
\end{enumerate}
\end{lemma}

>>>>

Note that since all three corollaries follow from Lemma~\ref{lem:concentration_argument}, Proposition~\ref{prop:concentration_argument_all} follows if we can prove that the conclusions from this lemma hold when we replace $\rho(y,k_n)$ with either $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$. For this the following, slightly more general version of Lemma~\ref{lem:concentration_argument} will be important.

\begin{lemma}\label{lem:concentration_argument_rho_approximation}
Let $\alpha > \frac{1}{2}, \nu > 0$ and $k_n \to \infty$ such that $k_n = \smallO{n}$, $\ell_n = (1 + \epsilon_n)k_n$, with $\epsilon_n \to 0$ and define
\[
	\lambda_n^\pm = (\ell_n \pm C \sqrt{\ell_n \log(\ell_n)}) \wedge \xi, \quad \text{and} \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi}\right).
\] 
In addition, define $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, where $\hat{\mu}_n(y)$ satisfies, 
\[
	\hat{\mu}_n(y) = (1 + \phi_n(y))\mu(y),
\]
where $\phi_n(y)$ is a continuously differentiable function such that
\begin{enumerate}[\upshape i)]
\item For some $0 < \varepsilon < 1$, $\displaystyle \lim_{n \to \infty} \sup_{0 \le y \le (1 - \varepsilon)R_n} |\phi_n(y)| = 0$,
\item $\displaystyle \lim_{n \to \infty}  \sup_{y \in \Kcal_{C}(\ell_n)} |\phi_n^\prime(y)| = 0.$
\end{enumerate}
Then the following holds.
\begin{enumerate}
\item For any continuous function $h : \R_+ \rightarrow  \R$, such that $h(y) = \bigO{e^{\beta y}}$ as $y \to \infty$ for some $\beta < \alpha$, 
\begin{equation}\label{eq:error_bound_int_rho_approx_not_K}
	\int_{\R_+ \setminus (a_n^-, a_n^+)} \hat{\rho}_n(y,k_n) h(y) \alpha e^{-\alpha y} \dd y
	= \bigO{k_n^{-(1+C^2)/2}},
\end{equation}
as $n \to \infty$.
\item If in addition, $h(a_n) \sim h(b_n)$ whenever $a_n \sim b_n$, as $n \to \infty$, then,
\begin{equation}\label{eq:concentration_h_rho_approx}
	\int_0^\infty h(y) \hat{\rho}_n(y,k_n) \alpha e^{-\alpha y} \dd y \sim  
		2\alpha \xi^{2\alpha} h(2\log(k_n/\xi)) k_n^{-(2\alpha + 1)},
\end{equation}
as $n \to \infty$.
\end{enumerate}
\end{lemma}

### 2019-03-12 proofs_finite_k.tex
improvements to section 4.2 and typos in Lemma 6.6

\subsection{Overall clustering coefficient, proving Theorem~\ref{thm:maincc}}
In this subsection, we want to infer that the clustering coefficient of the KPKVB random graph $c \xrightarrow{\Pee} \gamma$ by only using that $c(k) \xrightarrow{\Pee} \gamma(k)$ for fixed $k$.

\begin{proofof}{Theorem~\ref{thm:maincc}}
Let $\epsilon >0$.
First of all, from Equations~\ref{eq:def_pk}, \ref{eq:gammakint} and \ref{eq:gammaint}, we know that $\gamma = \sum_{k=2}^\infty \gamma(k)p_k$. In particular, we know that this series converges (we can use that $\gamma(k)\in [0,1]$ and $\sum_{k=0}^\infty p_k = 1$). Therefore, for $\delta >0$ with $\epsilon-2\delta>0$, there is $K_\delta$ such that $|\gamma - \sum_{k=2}^{K_\delta} \gamma(k)p_k| \leq \delta$. Furthermore, $c_n = \sum_{k=2}^\infty c_n(k)p_n(k)$, so by possibly choosing a larger value for $K_\delta$, we have that $|c_n-\sum_{k=2}^{K_\delta} c_n(k)p_n(k)| \leq \delta$.
Putting these observations together:
\begin{align*}
|c_n-\gamma| &\leq \left|c_n-\sum_{k=2}^{K_\delta}c_n(k)p_n(k)\right|+\left|\sum_{k=2}^{K_\delta} c_n(k)p_n(k) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| +\left|\sum_{k=2}^{K_\delta} \gamma(k)p_k-\gamma\right| \\
 &\leq \delta +\left|\sum_{k=2}^{K_\delta} c_n(k)p_n(k) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| +\delta 
\end{align*}
Therefore, $\Pee(|c_n-\gamma|\geq \epsilon) \leq \Pee(\left|\sum_{k=2}^{K_\delta} c_n(k)p_n(k) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| \geq \epsilon - 2\delta) \rightarrow 0$ because $c_n(k) \xrightarrow{\Pee} \gamma(k)$ for $k=2,\dots,K_\delta$ and $p_n(k) \xrightarrow{\Pee} p_k$ together imply that $\sum_{k=2}^{K_\delta} c_n(k)p_n(k) \xrightarrow{\Pee} \sum_{k=2}^{K_\delta} \gamma(k) p_k$. %p_k =  = \Theta(k^{-(2\alpha +1)})
\end{proofof}

>>>>

\subsection{Overall clustering coefficient, proving Theorem~\ref{thm:maincc}}
In this subsection, we want to infer that the clustering coefficient of the KPKVB random graph $c(G_n) \xrightarrow{\Pee} \gamma$ by using that $c(k;G_n) \xrightarrow{\Pee} \gamma(k)$ for fixed $k$.

\begin{proofof}{Theorem~\ref{thm:maincc}}
Let $\epsilon >2\delta >0$.
As the $p_k$ form the probability mass function of an $\N_0$-valued random variable, we have that $\sum_{k=0}^\infty p_k = 1$, which implies that there is $K_\delta >0$ such that $1-\delta < \sum_{k=0}^{K_\delta} p_k \leq 1$.
From Equations~\ref{eq:def_pk}, \ref{eq:gammakint} and \ref{eq:gammaint}, we know that $\gamma = \sum_{k=2}^\infty \gamma(k)p_k$. 
From this, it follows that $(1-\delta)\gamma < \sum_{k=2}^{K_\delta} \gamma(k) p_k \leq 1$ and hence that $|\gamma - \sum_{k=2}^{K_\delta} \gamma(k)p_k| \leq \delta$. Write $p(k;G_n)=\frac{N_n(k)}{n}$ for the fraction of degree $k$ vertices in the KPKVB model. From the definition of the clustering coefficient and function, it follows immediately that $c(G_n) = \sum_{k=2}^\infty c(k;G_n)p(k;G_n)$. By the initial observation, it follows again that $(1-\delta)c(k;G_n) < \sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) \leq 1$, and hence, $|c(G_n)-\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n)| \leq \delta$.
Putting these observations together:
\begin{align*}
|c(G_n)-\gamma| &\leq \left|c(G_n)-\sum_{k=2}^{K_\delta}c(k;G_n)p(k;G_n)\right|+\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| +\left|\sum_{k=2}^{K_\delta} \gamma(k)p_k-\gamma\right| \\
 &\leq \delta +\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| +\delta 
\end{align*}
Therefore, $\Pee(|c(G_n)-\gamma|\geq \epsilon) \leq \Pee(\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| \geq \epsilon - 2\delta) \rightarrow 0$ because $c(k;G_n) \xrightarrow{\Pee} \gamma(k)$ for $k=2,\dots,K_\delta$ and $p(k;G_n) \xrightarrow{\Pee} p_k$ together imply that $\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) \xrightarrow{\Pee} \sum_{k=2}^{K_\delta} \gamma(k) p_k$. %p_k =  = \Theta(k^{-(2\alpha +1)})
\end{proofof}
